quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-19 paper-quollr.Rmd
Added Figure title

Our algorithm includes the following steps: (1) scaling the NLDR data, (2) computing configurations of a hexagon grid, (3) binning the data, (4) obtaining the centroids of each bin, (5) indicating neighboring bins with line segments that connect the centroids, and (6) lifting the model into high dimensions. A detailed description of the algorithm can be found in **cite the methodology paper**.

@@

crosstalk::bscols(
    htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr 1fr 1fr 1fr; gap: 0;",
    htmltools::div(style = "margin: 0; padding: 0;", scurve_umap_plt_int),
    htmltools::div(style = "margin: 0; padding: 0;", hex_grid_poly_scurve_int),
    htmltools::div(style = "margin: 0; padding: 0;", hex_centroids_scurve_int),
    htmltools::div(style = "margin: 0; padding: 0;", wireframe_scurve_int),
    htmltools::div(
      style = "margin-top: 13px;t",
      scurve_umap_model_vis_n
    )),
    device = "xs"
  )
```

```{r, eval=knitr::is_latex_output(), out.width="100%", fig.height=5, fig.width=25, fig.pos='H', fig.cap="Key steps for constructing the model on the UMAP layout ($k=2$): (a) NLDR data, (b) hexagon bins, (c) bin centroids, (d) triangulated centroids, and (e) lifting the model into high dimensions. The `Scurve` data is shown."}
scurve_umap_plt + hex_grid_poly_scurve +
  hex_centroids_scurve + wireframe_scurve + 
  scurve_proj_umap_model1 +
  plot_layout(ncol = 5)
```

>>>>

Our algorithm includes the following steps: (1) scaling the NLDR data, (2) computing configurations of a hexagon grid, (3) binning the data, (4) obtaining the centroids of each bin, (5) indicating neighboring bins with line segments that connect the centroids, and (6) lifting the model into high dimensions ([Figure 2](#fig-algo-steps)). A detailed description of the algorithm can be found in **cite the methodology paper**.

@@

htmltools::browsable(
  tagList(
    tags$div(
      id = "fig-algo-steps",  # This is the anchor
      crosstalk::bscols(
        htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr 1fr 1fr 1fr; gap: 0;",
                       htmltools::div(style = "margin: 0; padding: 0;", scurve_umap_plt_int),
                       htmltools::div(style = "margin: 0; padding: 0;", hex_grid_poly_scurve_int),
                       htmltools::div(style = "margin: 0; padding: 0;", hex_centroids_scurve_int),
                       htmltools::div(style = "margin: 0; padding: 0;", wireframe_scurve_int),
                       htmltools::div(
                         style = "margin-top: 13px;t",
                         scurve_umap_model_vis_n
                       )),
        device = "xs"
      ),
      tags$p(tags$strong("Figure 2:"), "Key steps for constructing the model on the UMAP layout: (a) NLDR data, (b) hexagon bins, (c) bin centroids, (d) triangulated centroids, and (e) lifting the model into high dimensions. The `Scurve` data is shown.")
    )
  )
)
```

```{r, eval=knitr::is_latex_output(), out.width="100%", fig.height=5, fig.width=25, fig.pos='H', fig.cap="Key steps for constructing the model on the UMAP layout: (a) NLDR data, (b) hexagon bins, (c) bin centroids, (d) triangulated centroids, and (e) lifting the model into high dimensions. The `Scurve` data is shown."}
scurve_umap_plt + hex_grid_poly_scurve +
  hex_centroids_scurve + wireframe_scurve + 
  scurve_proj_umap_model1 +
  plot_layout(ncol = 5)
```

### 2025-05-19 paper-quollr.tex
Added Figure title

Our algorithm includes the following steps: (1) scaling the NLDR data, (2) computing configurations of a hexagon grid, (3) binning the data, (4) obtaining the centroids of each bin, (5) indicating neighboring bins with line segments that connect the centroids, and (6) lifting the model into high dimensions. A detailed description of the algorithm can be found in \textbf{cite the methodology paper}.

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-5-1} \caption{Key steps for constructing the model on the UMAP layout ($k=2$): (a) NLDR data, (b) hexagon bins, (c) bin centroids, (d) triangulated centroids, and (e) lifting the model into high dimensions. The `Scurve` data is shown.}\label{fig:unnamed-chunk-5}
\end{figure}

>>>>

Our algorithm includes the following steps: (1) scaling the NLDR data, (2) computing configurations of a hexagon grid, (3) binning the data, (4) obtaining the centroids of each bin, (5) indicating neighboring bins with line segments that connect the centroids, and (6) lifting the model into high dimensions (\hyperref[fig-algo-steps]{Figure 2}). A detailed description of the algorithm can be found in \textbf{cite the methodology paper}.

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-5-1} \caption{Key steps for constructing the model on the UMAP layout: (a) NLDR data, (b) hexagon bins, (c) bin centroids, (d) triangulated centroids, and (e) lifting the model into high dimensions. The `Scurve` data is shown.}\label{fig:unnamed-chunk-5}
\end{figure}
